Tool-driven Revolutions in Archaeological Science

### 2018-12-18 analysis/paper/jcaa-paper.Rmd
forgotten word

```{r ecology-articles-citing-r-plot, fig.cap=str_glue('Number of articles per year citing R in top Ecology journals ({prettyNum(articles_shown_in_plot,",")} articles out of {prettyNum(how_many_articles_in_top_journals_for_cran_cites,",")}). Data from Web of Science for 2007-2017')}
min_y <- 2007
max_y <- 2025
all_sciences_citing_R_over_time <- 
ggplot(cran_cites_all_areas_top_journals_by_year,
       aes(PY,
           prop,
           colour = SO)) +
  geom_line(size = 2) +
  geom_text_repel(
    data = subset(cran_cites_all_areas_top_journals_by_year, 
                  PY == max(PY)),
    aes(label = str_wrap(SO_n, 40)),
    size = 4,
    nudge_x = 0,
    hjust = 0,
    segment.color = NA,
    direction = "y"
  ) +
   scale_x_continuous(breaks = min_y:max_y,
                     labels = c(min_y:2017, rep("", length(2018:max_y))),
                     limits = c(min_y, max_y)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Publication year") +
  ylab("Percentage of articles in that journal in that year") +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

@@

```{r text-mining-article-titles-archaeology-plot, fig.cap=paste0("Comparing the frequency of words used in titles \nof archaeology articles (", prettyNum(nrow(frequency)), " words in ", prettyNum(nrow(archy_journal_articles)), " articles)")}

@@

```{r archaeology-reproducible-articles-plot, fig.cap=paste0('Articles in archaeology journals\nusing R for reproducible research (n = ', number_of_reproducible_articles,')')}

>>>>

```{r ecology-articles-citing-r-plot, fig.cap=str_glue('Percentage of articles per year citing R in top Ecology journals ({prettyNum(articles_shown_in_plot,",")} articles out of {prettyNum(how_many_articles_in_top_journals_for_cran_cites,",")}). Data from Web of Science for 2007-2017')}
min_y <- 2007
max_y <- 2025
all_sciences_citing_R_over_time <- 
ggplot(cran_cites_all_areas_top_journals_by_year,
       aes(PY,
           prop,
           colour = SO)) +
  geom_line(size = 2) +
  geom_text_repel(
    data = subset(cran_cites_all_areas_top_journals_by_year, 
                  PY == max(PY)),
    aes(label = str_wrap(SO_n, 40)),
    size = 4,
    nudge_x = 0,
    hjust = 0,
    segment.color = NA,
    direction = "y"
  ) +
   scale_x_continuous(breaks = min_y:max_y,
                     labels = c(min_y:2017, rep("", length(2018:max_y))),
                     limits = c(min_y, max_y)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Publication year") +
  ylab("Percentage of articles in that journal in that year") +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

@@

```{r text-mining-article-titles-archaeology-plot, fig.cap=str_glue("Comparing the frequency of words used in titles \nof archaeology articles (", prettyNum(nrow(frequency)), " words in ", prettyNum(nrow(archy_journal_articles)), " articles)")}

@@

```{r archaeology-reproducible-articles-plot, fig.cap=str_glue('Articles in archaeology journals\nusing R for reproducible research (n = ', number_of_reproducible_articles,')')}
